Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-06 code/rmarkdown/article.Rmd
+ fixes to stats + written more of results section + fixed all tables + in processing of fixing figures

We fit two sets of generalized linear models (GLM) with logit links. The first set of models were fit to the proportion of adaptive genetic variation and environmental variation secured in each prioritization for each species associated with adaptive loci. Similarly, the second set of models assessed the relationship between the proportion of neutral genetic variation and the geographic variation secured in each prioritization for each species. We conducted likelihood ratio tests between each model and its corresponding null model, and applied Bonferroni corrections to assess significance. To assess the effectiveness of these variables as surrogates, we computed the Cragg and Uhler's pseudo-R$^2$ value for each model [using the \texttt{pscl} R package; @r492].

@@

<!-- correlation analysis -->
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated;_P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next logical step was to determine how effective these variables were as surrogates.

<!-- surrogacy analysis -->

>>>>

We fit two full generalized linear models (GLM) with a logit links. The first model was fit to the proportion of adaptive genetic variation secured in a prioritization, and contained a continuous predictor variable measuring the proportion of environmental variation also secured in the prioritization, a categorical variable indicating the species for which the prioritization was generated, and an interaction term between these predictor variables. The second model was fit to the proportion of neutral genetic variation secured in a prioritization, and contained a continuous predictor variable assessing the proportion of geographic variation also secured in the prioritization. Similar to the previous model, this model also contained a predictor variable indicating the species for which the prioritizations were generated, and an interaction term. We subject these models to a backwards step-wise term deletion routine to assess term significance. To assess the performance of these surrogates, we fit a suite of models correlating the proportion of adaptive and neutral genetic variation held in each prioritization and the environmental and geographic variation they also secured (respectively). We then computed the Cragg and Uhler's pseudo-R$^2$ value for each model [using the \texttt{pscl} R package; @r492].

@@

<!-- correlation analysis -->
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated;_P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next step was to determine how effective these variables were as surrogates in the context of conservation planning.
The dissimilarity matrices generated using the surrogate variables correlated with the dissimilarity matrices based on the genetic characteristics of individuals for most species (Table 1). Specifically, environmental variation was found to significantly correlate with adaptive genetic variation for `r sum(correlation.model.summary.DF$Environmental.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Environmental.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Environmental.corr.P)))*100,2)` % associated with loci under selection; _P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Environmental.corr.P<0.05)$Environmental.Marginal.R2),2)` SD for significant models). Additionally, geographic distances between planning units were found to significantly correlate with neutral genetic variation among planning units for `r sum(correlation.model.summary.DF$Geographic.corr.P<0.05,na.rm=TRUE)` species (`r round((sum(correlation.model.summary.DF$Geographic.corr.P<0.05)/length(na.omit(correlation.model.summary.DF$Geographic.corr.P)))*100,2)` % of all the species investigated;_P_ < 0.05; mean marginal `r round(mean(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` $R^2$ $\pm$ `r round(sd(filter(correlation.model.summary.DF, Geographic.corr.P<0.05)$Geographic.Marginal.R2),2)` SD for significant models). These results suggest that prioritizations with different environmental characteristics tend to have individuals with different adaptive genetic characteristics. Similarly, planning units that are further apart tend to have individuals with different neutral genetic characteristics. After verifying that the geographic and environmental variables correlate with genetic variation, the next step was to determine how effective these variables were as surrogates in the context of conservation planning.

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated ($\chi^2_{`r env.surrogacy.AOV$Resid..Dev[[4]]`} P = `r env.surrogacy.AOV$Pr..Chi.[[4]]`$). The slope for each species were all significantly different to zero (minimum $z value = `r min(env.surrogate.spp.DF$statistic)`$; maximum $P = r `max(env.surrogate.spp.DF$p.value)`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r mean(env.surrogate.spp.DF$r2CU)` $R^2$ `r sd(env.surrogate.spp.DF$r2CU)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization ($\chi^2_{`r geo.surrogacy.AOV$Resid..Dev[[4]]`} P = `r geo.surrogacy.AOV$Pr..Chi.[[4]]`$). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r mean(geo.surrogate.spp.DF$r2CU)` $R^2$ `r sd(geo.surrogate.spp.DF$r2CU)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

### 2016-05-06 code/rmarkdown/figures.Rmd
+ fixes to stats + written more of results section + fixed all tables + in processing of fixing figures

p1.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Environmental')) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

p2.hist <- ggplot(aes(R2),
		data=filter(surrogacy.model.summary.DF, Type=='Geographic')) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of geographic', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=0.05, y=0.95, label='(d)') +
		coord_cartesian(xlim=c(0, 1))

@@

>>>>

p1.hist <- ggplot(aes(r2CU),
		data=filter(env.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of environmental', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'),
		plot.background=element_rect(fill='transparent', colour='transparent')) +
		geom_text(x=0.05, y=0.95, label='(c)') +
		coord_cartesian(xlim=c(0, 1))

p2.hist <- ggplot(aes(r2CU),
		data=filter(geo.surrogate.spp.DF, !is.na(r2CU))) +
	geom_histogram(fill='grey10', bins=10) +
	ylab('\nFrequency') + xlab(expression(atop('Effectiveness of geographic', variables~(R^2~coefficient)))) +
	theme_classic() + theme(axis.line.x=element_line(color='black'),
		axis.line.y=element_line(color='black'), 
		plot.background=element_rect(fill='transparent')) +
		geom_text(x=0.05, y=0.95, label='(d)') +
		coord_cartesian(xlim=c(0, 1))

@@

#### Supplementary info figures

```{r, echo=FALSE, message=FALSE, warnings=FALSE, fig.width=8, fig.height=8, fig.cap='The relationship between the proportion of adaptive genetic variation secured in a prioritizaiton and the proportion of environmental variation it also secures. Points represent values associated with randomly generated prioritizations. Black lines indicate average trends computed using generalised linear models with logit links. Each panel corresponds to different species.'}
# format data
curr.DF <- env.surrogacy.DF %>% filter(!is.na(genetic.held))
curr.DF2 <- env.surrogate.spp.DF %>% filter(!is.na(r2CU))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0.05
curr.DF2$genetic.held <- 0.95

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=1)) +
		xlab('Environmental variation secured (%)') +
		ylab('Adaptive genetic variation secured (%)') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_point(fill='transparent') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=1, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, fig.width=8, fig.height=8, fig.cap='The relationship between the proportion of neutral genetic variation secured in a prioritizaiton and the proportion of geographic variation it also secures. Conventions are detailed in Figure SXXX.'}
# format data
curr.DF <- geo.surrogacy.DF %>% filter(!is.na(genetic.held))
curr.DF2 <- geo.surrogate.spp.DF %>% filter(!is.na(r2CU))
curr.DF2$R2_repr <- round(curr.DF2$r2CU,2)
curr.DF2$R2_repr <- sapply(curr.DF2$R2_repr, function(x) {as.character(as.expression(substitute(~~italic(R)^2~"="~r2, list(r2=x))))})
curr.DF2$surrogate.held <- 0.05
curr.DF2$genetic.held <- 0.95

# make plot
suppressWarnings(
	ggplot(aes(x=surrogate.held, y=genetic.held), data=curr.DF) +
		theme_classic() +
		theme(strip.background=element_rect(fill='grey20'), strip.text=element_text(color='white', face='italic', size=1)) +
		xlab('Geographic variation secured (%)') +
		ylab('Neutral genetic variation secured (%)') +
		stat_smooth(method='glm', method.args=list(family='binomial'), fullrange=TRUE,
			se=FALSE, color='blue') +
		geom_point(fill='transparent') +
		geom_text(aes(label=R2_repr), data=curr.DF2, parse=TRUE, hjust=0, size=1, color='blue') +
		facet_wrap(~ Species, ncol=4)
)
```

### 2016-05-06 code/rmarkdown/supporting_information.Rmd
+ fixes to stats + written more of results section + fixed all tables + in processing of fixing figures

```{r, echo=FALSE}
## make results table showing Eigen values
knitr::kable(
	pca.DF,
	digits=2,
	caption=paste0('Summary of principle components analysis (PCA) on bioclimatic variation across the study area. The first ',as.character(as.english(surrogate.params.LST[[MODE]]$number.components)),' principle components (PCs) were used for subsequent analysis.'),
	align=c('c', 'c', 'c', 'c')
)
```

```{r, echo=FALSE}
knitr::kable(
	format.dataframe(
		filter(spp.nmds.summary.DF,!is.na(Stress)),
		omit=c('Loci','Converged')
	),
	digits=2,
	caption='Summary of non-metric multi-dimensional scaling (MDS) analyses on genetic variation for each species. The analyses were used to identify the main gradients of variation in binary binary adaptive and neutral loci data.',
	col.names=c('Species', 'Loci Type', 'K', 'NMDS Stress', 'Converged'),
	align=c('c', 'c', 'c', 'c', 'c')
)
```

>>>>

### insert figures here

```{r, echo=FALSE, results='asis'}
## make results table showing Eigen values
curr.file <- tempfile(fileext='.tex')
pca.DF[['Eigen Value']] <- c(round(pca.DF[['Eigen Value']][-19],2), pvalString(pca.DF[['Eigen Value']][19], digits=2))
pca.DF[['Variation explained (%)']] <- c(round(pca.DF[['Variation explained (%)']][1:3],2), pvalString(pca.DF[['Variation explained (%)']][-1:-3], digits=2))
pca.DF[['Accumulative variation explained (%)']] <- as.character(round(pca.DF[['Accumulative variation explained (%)']],2))
x <- pca.DF %>%
	latex(file=curr.file, 
		rowname=NULL, first.hline.double=FALSE, booktabs=TRUE, col.just=rep('c', ncol(pca.DF)), here=TRUE,
		colheads=c("\\parbox[t]{2.5cm}{\\centering \\bfseries{Principle Component}}", "\\parbox[t]{2cm}{\\centering \\bfseries{Eigen value}}",
			"\\parbox[t]{3cm}{\\centering \\bfseries{Variation explained (\\%)}}", "\\parbox[t]{4.5cm}{\\centering \\bfseries{Cumulative variation explained (\\%)}}"),
		caption=paste0('Summary of principle components analysis (PCA) on bioclimatic variation across the study area. The first ',as.character(as.english(surrogate.params.LST[[MODE]]$number.components)),' principle components (PCs) were used for subsequent analysis.')
	)
readLines(curr.file)[-1] %>% paste0(collapse='\n') %>% 
	gsub(pattern='toprule', replacement='toprule[1pt]', fixed=TRUE) %>%
	gsub(pattern='bottomrule', replacement='bottomrule[1pt]', fixed=TRUE) %>%
	cat()
```

```{r, echo=FALSE, results='asis'}
adaptive.spp.nmds.summary.DF <- spp.nmds.summary.DF %>% filter(Loci=='adaptive') %>% mutate(Stress=pvalString(Stress))
neutral.spp.nmds.summary.DF <- spp.nmds.summary.DF %>% filter(Loci=='neutral') %>% mutate(Stress=pvalString(Stress))
names(adaptive.spp.nmds.summary.DF)[2:5] <- paste0('adaptive.', names(adaptive.spp.nmds.summary.DF)[2:5])
names(neutral.spp.nmds.summary.DF)[2:5] <- paste0('neutral.', names(neutral.spp.nmds.summary.DF)[2:5])
spp.nmds.summary.DF2 <- full_join(adaptive.spp.nmds.summary.DF, neutral.spp.nmds.summary.DF, by='Species')
spp.nmds.summary.DF2$adaptive.Stress[which(spp.nmds.summary.DF2$adaptive.Converged)] <- paste0('\\bfseries{', spp.nmds.summary.DF2$adaptive.Stress[which(spp.nmds.summary.DF2$adaptive.Converged)],'}')
spp.nmds.summary.DF2$neutral.Stress[which(spp.nmds.summary.DF2$neutral.Converged)] <- paste0('\\bfseries{', spp.nmds.summary.DF2$neutral.Stress[which(spp.nmds.summary.DF2$neutral.Converged)],'}')
spp.nmds.summary.DF2 <- spp.nmds.summary.DF2 %>%
	mutate(blank='') %>%
	select(Species, adaptive.k:adaptive.Stress, neutral.k:neutral.Stress)
curr.file <- tempfile(fileext='.tex')
x <- spp.nmds.summary.DF2 %>%
	latex(
		file=curr.file,
		rowname=NULL, first.hline.double=FALSE, booktabs=TRUE, col.just=rep('c', 5),
		cgroup=c('', 'Adaptive', 'Neutral'), n.cgroup=c(1, 2, 2),
		colheads=c('\\bfseries{Species}', 'K', 'Stress', 'K', 'Stress'), here=TRUE,
		caption='Summary of non-metric multi-dimensional scaling (NMDS) analyses on genetic variation for each species. The analyses were used to identify the main graondients of variation in binary adaptive and neutral loci data. Bold stress values indicate NMDS analyses that have converged.'
	)
readLines(curr.file)[-1] %>% paste0(collapse='\n') %>% 
	gsub(pattern='\\cline{1-', replacement='\\cline{3-4} \\cline{6-', fixed=TRUE) %>% 
	gsub(pattern='toprule', replacement='toprule[1pt]', fixed=TRUE) %>%
	gsub(pattern='bottomrule', replacement='bottomrule[1pt]', fixed=TRUE) %>%
	cat()
```

```{r, echo=FALSE, results='asis'}
curr.file <- tempfile(fileext='.tex')
x <- surrogate.spp.DF %>%
	mutate(
		Environmental.z = paste(round(Environmental.estimate,2), '$\\pm$', round(Environmental.std.error,2)),
		Geographic.z = paste(round(Geographic.estimate,2), '$\\pm$', round(Geographic.std.error,2)),
		Species = paste0('\\textit{', gsub('_', ' ', Species, fixed=TRUE), '}')) %>%
	select(Species, Environmental.z, Environmental.p.value, Environmental.r2CU,
		Geographic.z, Geographic.p.value, Geographic.r2CU) %>%
	latex(file=curr.file, 
		cgroup=c('', 'Environmental', 'Geographic'), n.cgroup=c(1, 3, 3), col.just=rep('c', 7),
		digits=2, rowname=NULL, first.hline.double=FALSE, booktabs=TRUE, here=TRUE,
		colheads=c('\\bfseries{Species}', '$\\textit{Z}$', '\\textit{P}', '$R^2$', '$\\textit{Z}$', '\\textit{P}', '$R^2$'),
		caption='Summary of post-hoc analyses on generalized linear models. Briefly, two generalized linear models were fit to correlate the proportion of adaptive genetic variation and environmental variation secured, and the proportion of neutral genetic variation and geographic variation secured in a prioritization. These models also included a predictor variable indicating the species for which the prioritizations were generated, and an interaction term. A post-hoc analysis was conducted to determine if the slopes for each species were significantly different to zero (detailed in the \\textit{Z} and \\textit{P} columns). All tests used a single degree of freedom. Cragg and Uhler\'s pseudo-R$^2$ values were calculated to show the proportion of variation explained by the slopes for each species ($R^2$ column).'
	)
readLines(curr.file)[-1] %>% paste0(collapse='\n') %>% 
	gsub(pattern='\\cline{1-', replacement='\\cline{2-5} \\cline{7-', fixed=TRUE) %>% 
	gsub(pattern='ulticolumn{1}{c}{$R^2$}\\tabularnewline', replacement='ulticolumn{1}{c}{$R^2$}\\T\\B\\tabularnewline', fixed=TRUE) %>% 
	gsub(pattern='toprule', replacement='toprule[1pt]', fixed=TRUE) %>%
	gsub(pattern='bottomrule', replacement='bottomrule[1pt]', fixed=TRUE) %>%
	cat()
```

### 2016-05-06 code/rmarkdown/tables.Rmd
+ fixes to stats + written more of results section + fixed all tables + in processing of fixing figures

# set options
options(error=NULL)

```

## Tables

```{r, echo=FALSE}
knitr::kable(
	format.dataframe(correlation.DF),
	digits=2,
	caption='Correlation between surrogate variables and genetic variation. The $R^2$ columns show the proportion of genetic variation explained by surrogates. Specifically, marginal $R^2$ represents the proportion of variation explained by the fixed effects alone. The conditional $R^2$ represents the proportion of variation explained by the fixed and random effects. All $\\chi^2$ tests were based on one degree of freedom. Significant $P$ values ($P$ < 0.05) indicate that surrogate variables correlate with genetic variation.',
	col.names=c('Species', 'Test', 'Marginal $R^2$', 'Conditional $R^2$', '$\\chi^2$', '\\textit{P}'),
	align=rep('c', ncol(correlation.DF)),
)
```

>>>>

# set options
options(error=NULL)
```
## Tables

```{r, echo=FALSE, results='asis'}
curr.file <- tempfile(fileext='.tex')
x <- correlation.model.summary.DF %>%
	select(-contains('raw')) %>%
	mutate(
		Environmental.corr.P=pvalString(Environmental.corr.P),
		Geographic.corr.P=pvalString(Geographic.corr.P), 
		blank=rep('', length(Species)),
		Species=paste0('\\textit{', gsub('\\ ', ' ', Species), '}')) %>%
	select(Species:Environmental.corr.P, Geographic.Marginal.R2:Geographic.corr.P) %>%
	latex(file=curr.file, 
		cgroup=c('', 'Environmental', 'Geographic'), n.cgroup=c(1, 4, 4), col.just=rep('c', 9),
		digits=2, rowname=NULL, first.hline.double=FALSE, booktabs=TRUE, here=TRUE,
		colheads=c('\\bfseries{Species}', '$MR^2$', '$CR^2$', '$\\chi^2$', '\\textit{P}', '$MR^2$', '$CR^2$', '$\\chi^2$', '\\textit{P}'),
		caption='Summary of maximum likelihood population-effects (MLPE) models. Briefly, for each species associated with adaptive loci, a model was fit to correlate dissimilarities among planning units where the species in terms of the adaptive genetic characteristics of individuals in them with dissimilarities in terms of the environmental conditions inside the planning units (denoted in the environmental column group). Similarly, for each species, a model was fit to correlate dissimilarities among the planning units in terms of the neutral genetic characteristics of indiviudals in them with dissimilarities in terms of the geographic position of the planning units (denoted in the geographic column group). Data shows the marginal $R^2$ ($MR^2$) and conditional $R^2$ ($CR^2$) for each model, and also the results from comparing the models to their corresponding null models. All $\\chi^2$ tests had 1 degree of freedom.'
	)
readLines(curr.file)[-1] %>% paste0(collapse='\n') %>% 
	gsub(pattern='\\cline{1-', replacement='\\cline{2-6} \\cline{8-', fixed=TRUE) %>% 
	gsub(pattern='{c}{\\textit{P}}\\tabularnewline', replacement='{c}{\\textit{P}}\\T\\B\\tabularnewline', fixed=TRUE) %>% 
	gsub(pattern='toprule', replacement='toprule[1pt]', fixed=TRUE) %>%
	gsub(pattern='bottomrule', replacement='bottomrule[1pt]', fixed=TRUE) %>%
	cat()
 ```
